---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidydifference

<!-- badges: start -->
<!-- badges: end -->

## Overview

Tidydifference is a small utility to draw difference plots (aka Bland-Altman plots). It aims to have a tidy interface

## Installation

You can install the development version of tidydifference like so:

``` r
# install.packages("devtools")
devtools::install_github("divinenephron/tidydifference")
```

## Usage

Plot the absolute difference (default) against the mean result (default).

```{r usage_1}
library(tidydifference)
difference_plot(hidx_eqa, sample_col = sample, result_col = h_index, analyser_col = analyser)
```

Plot the relative difference against the EQA method mean (which we've recorded as if it were an analyser).

```{r usage_2}
difference_plot(hidx_eqa, sample_col = sample, result_col = h_index, analyser_col = analyser, comparison = "EQA Method Mean", difference = "relative")
```
